The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-25 article.tex
\ref is for referecing, \label for defining labels
Typo fix

CTfile Sgroups capture and organise high level information about sets of atoms
and bonds~\cite{Gushurst91}. There are four types of Sgroup: Display Shortcuts, Polymers,
Mixtures, and Data. The most familiar Sgroups from an end user perspective are structure 
repeat units (e.g. bracketing) and abbreviations (Figure~8\label{fig:sgroups}). CDK \cdkversion{} adds 
supports for representation, reading, writing, and depiction.

@@

As the library grew over the years, so did the complexity of the maintenance:
Increasingly frequent, the main branch faied to compile, and bug fixing become
more difficult with unexpected side effects. Often fixing a bug in one part of
the code, broke some other code which made the incorrect assumptions about the
fixed code. Such is inevitable when the number of developers increases.

>>>>

CTfile Sgroups capture and organise high level information about sets of atoms
and bonds~\cite{Gushurst91}. There are four types of Sgroup: Display Shortcuts, Polymers,
Mixtures, and Data. The most familiar Sgroups from an end user perspective are structure 
repeat units (e.g. bracketing) and abbreviations (Figure~8\ref{fig:sgroups}).
CDK~\cdkversion{} adds 
supports for representation, reading, writing, and depiction.

@@

As the library grew over the years, so did the complexity of the maintenance:
Increasingly frequent, the main branch failed to compile, and bug fixing become
more difficult with unexpected side effects. Often fixing a bug in one part of
the code, broke some other code which made the incorrect assumptions about the
fixed code. Such is inevitable when the number of developers increases.
